Models

### 2021-08-03 analysis/05_model_metrics.Rmd
Modify function for extracting slopes for random effects levels to generalize for all random effects, not just study.

  tidy(fit$result) %>%
   mutate(metric = metric_name, model = list(fit), model_id = model_id, warning = ifelse(length(fit$warnings) == 0, NA, fit$warnings))
}

@@

Get study level slope estimates
```{r}
get_study_slopes <- function(metric, model){
  year_scaled_coef <- tidy(model) %>%
    filter(term == "year_scaled")

@@

  study_ests <- broom.mixed::tidy(model, effects="ran_vals") %>%
    filter(group == "study_id", term == "year_scaled") %>% 
    select(-c(effect, group, term)) %>%
    rename(study_id = level, cond.std.error = std.error, cond.estimate = estimate) %>%
    mutate(estimate = cond.estimate + year_scaled_est,
      cond.var = cond.std.error*cond.std.error, 
           var = cond.var + year_scaled_var,
           std.error = sqrt(var),
           upr.ci = estimate + (2*std.error),
           lwr.ci = estimate - (2*std.error),
           sig = case_when(
             lwr.ci < 0 & upr.ci > 0 ~ TRUE,
             TRUE ~ FALSE
           ),
           metric = metric)
}

study_slopes <- pmap_dfr(select(metric_model_table,  metric, model), get_study_slopes)

slopes_wide <- study_slopes %>%
  select(study_id, metric, estimate) %>%
  pivot_wider(names_from = "metric", values_from = "estimate")
```

>>>>

  tidy(fit$result) %>%
   mutate(metric = metric_name, model = list(fit$result), model_id = model_id, warning = ifelse(length(fit$warnings) == 0, NA, fit$warnings))
}

@@

Get study level slope estimates
```{r}
get_study_slopes <- function(metric, model, model_id){

  filter_name <- ifelse(model_id == "base", "study_id", model_id)

  year_scaled_coef <- tidy(model) %>%
    filter(term == "year_scaled")

@@

  study_ests <- broom.mixed::tidy(model, effects="ran_vals") %>%
    filter(group == filter_name, term == "year_scaled") %>% 
    select(-c(effect, group, term)) %>%
    #rename({{ model_id }} := level, cond.std.error = std.error, cond.estimate = estimate) %>%
    rename(cond.std.error = std.error, cond.estimate = estimate) %>%
    mutate(estimate = cond.estimate + year_scaled_est,
      cond.var = cond.std.error*cond.std.error, 
           var = cond.var + year_scaled_var,
           std.error = sqrt(var),
           upr.ci = estimate + (2*std.error),
           lwr.ci = estimate - (2*std.error),
           sig = case_when(
             lwr.ci < 0 & upr.ci > 0 ~ TRUE,
             TRUE ~ FALSE
           ),
      metric = metric,
      model_id = model_id)
}

model_df <- metric_model_table %>%
  select(metric, model, model_id) %>%
  group_by(metric, model_id) %>% 
  slice_head()

study_slopes <- pmap_dfr(model_df, get_study_slopes)

study_slopes_wide <- study_slopes %>%
  filter(model_id == "base") %>%
  select(study_id = level, metric, estimate) %>%
  pivot_wider(names_from = "metric", values_from = "estimate")
```
